---
title: "Jessie D. Ausman"
author: Jessie D. Ausman
date: "`r Sys.Date()`"
output:
    pagedown::html_resume:
      self-contained: false
---

```{r initial_setup, echo=FALSE, results = 'asis'}

source('helper_functions.R')

skill_data <- data.frame(skill = c("Excel", "R", "SQL", "Power BI", "Tableau", "(Git) Bash", "CSS", "JavaScript", "Python"), level = c(10, 9, 9, 8, 7, 7, 4, 3, 2))

```

```{js move_disclaim, echo=FALSE}
(function() {
  var pages
  var timer = 0;
  var changeDC = setInterval(function() {
  pages = document.querySelectorAll('.pagedjs_page');
  if(pages.length !== 2 && timer <= 5000) {
  timer += 200
  return;
}
if(pages.length !== 2 && timer > 5000) return clearInterval(changeDC);
var firstPage = pages[0];
var lastPage = pages[pages.length - 1];
var aside = firstPage.querySelector('#aside');
var asideClone = aside.cloneNode();
asideClone.id = "aside_last";
var disclaim = document.querySelector('#disclaimer');
asideClone.appendChild(disclaim);
lastPage.querySelector('.pagedjs_page_content > div').appendChild(asideClone);
clearInterval(changeDC);
}, 200);
})()
```

# Aside

*Skilled Analyst with 4 years of professional experience, including analyses of performance metrics, lab data, patient and other health data. Especially proficient in SQL, R, Tableau and Power BI with proven ability to lead innovative solutions, manage databases, train personnel in R and transform complex data into actionable insights, saving time and improving health outcomes.*

## Contact Info {#contact}

-   <i class="fa fa-envelope"></i> [jessaus1305\@gmail.com](mailto:jessaus1305@gmail.com){.email}
-   <i class="fa fa-github"></i> [github.com/JessAus](https://github.com/JessAus)
-   <i class = "fa fa-linkedin"></i> [LinkedIn](https://www.linkedin.com/in/jessie-ausman-b6a67a237/)
-   <i class = "fa fa-phone"></i> 817-528-5464

## Skills {#skills}

-   R Package Development
-   Quarto / RMarkdown
-   Shiny App Development
-   Data Visualization
-   Data Analysis
-   API Integration
-   Process Automation
-   Git / GitHub
-   PostgreSQL / SQL / T-SQL
-   Snowflake
-   QuickBase
-   Database Management
-   Project Management
-   ETL Skills
-   Familiarity with Snomed/LOINC 
-   SharePoint

# Main

## Jessie Ausman {#title}

### *Data Analyst, Public Health Professional*

## Experience {data-icon="laptop"}

### Public Health Informatics Analyst

Tarrant County Public Health Department

Fort Worth, TX (Hybrid)

2022--Present

-   Completed daily public analyses, ad hoc data requests and disease reporting
-   Started and manage the first Postgres database for the Informatics division
-   Designed a Shiny application for point-and-click database querying for personnel with limited R/SQL experience
-   Combined SQL/APIs to extract data, R to transform, analyze and create data reports and Task Scheduler to automate repeated processes, saving the organization 5+ hours per week on reporting
-   Documented >15 daily processes using RMarkdown and Quarto
-   Performed record linkage/de-duplication for large data (1.5+ million observations)
-   Trained >20 employees in R for data analyses, disease investigation processes and data entry/management
-   Saved investigators 10 hours/week tracking performance metrics by creating an interactive report capable of tracking these metrics automatically
-   Visualized & summarized data using Power BI, Flexdashboard (R), and Quarto (R)
-   Conducted vaccine-preventable and foodborne disease investigations

### Graduate Research Assistant

UNTHSC, Center for Older Adults

Fort Worth, TX (Hybrid)

2020--2022

-   Acted as IT/Data Entry for zoom-based, Project ECHO education programs; called recruited 25+ nursing homes to the program
-   Conducted literature reviews and summarized data for 3 separate grant proposals using SAS, Excel and R
-   Extracted, cleaned, analyzed and visualized clinical, demographic, and training data and summarized findings to program leadership using R, SAS, SQL and Tableau
-   Conducted an analysis of barriers to care among Wellmed patient population, identified top 5 barriers to care and provided recommendations to address barriers to care based on well-established best practices for intervention

### Research Technician

University of Texas at Arlington

Arlington, TX

2019--2020

-   Collected, organized, analyzed and presented scientific findings related to research on antimicrobial resistances
-   Conducted research in infectious microbes
-   Analyzed research data for publication using R and Excel

## Education {data-icon="graduation-cap" data-concise="true"}

### Certified in Public Health (CPH)

Certification awarded to MPH graduates who pass the CPH exam administered by NBPHE

Fort Worth, TX

2022--Present

### University of North Texas Health Science Center (UNTHSC)

Master's of Public Health (Epidemiology Concentration) \| Dean's List

Fort Worth, TX

2020--2022

### University of Texas at Arlington

Bachelor's of Science, Microbiology \| Summa Cum Laude Honors

Arlington, TX

2017--2019

<!-- ## Extracurricular Activities & Honors {data-icon="suitcase"} -->

<!-- ### School of Public Health Student Ambassador -->

<!-- University of North Texas Health Science Center -->

<!-- Fort Worth, TX -->

<!-- 2021--2022 -->

<!-- -   Nomination-based student organization -->
<!-- -   Duties of members include: acting as tour guides, panelists in student preview day events, and mentors to prospective students -->

<!-- ### Quality Control Volunteer -->

<!-- Tarrant Area Food Bank -->

<!-- Fort Worth, TX -->

<!-- 2019--2022 -->

<!-- -   Collaborate in teams to ensure the safety of foods being delivered to Tarrant County residents -->

<!-- ### Tarrant County Medical Reserve Corps (MRC) -->

<!-- Tarrant County Public Health Department -->

<!-- Fort Worth, TX -->

<!-- 2020 -->

<!-- -   Collected and entered patient information into eClinicalWorks (eCW) system to assist in local COVID-19 response during the pandemic -->

## Presentations/Publications {data-icon="comment-alt"}

### Using Open-Source Software (RStudio, R Shiny, & PostgreSQL) to Promote Data Modernization in Public Health

Council for State and Territorial Epidemiologists (CSTE) Conference 2024 \| Presenter, Author

Pittsburgh, PA

### Advancing the Knowledge, Skills and Abilities of the Long-term Care Workforce Through the Project ECHO Platform to Improve the Health of Older Adults

Texas Public Health Association (TPHA) 2022 \| Presenter, Author

Fort Worth, TX

### Septal Class A Penicillin-Binding Protein Activity and LD-Transpeptidases Mediate Selection of Colistin-Resistant Lipooligosaccharide-Deficient Acinetobacter baumannii

American Society for Microbiology (ASM) 2021 \| Co-author

Arlington, TX

```{css, echo=FALSE}
.extra-sidebar {
  top: 0;
  padding-top: 0;
}

.extra-sidebar h1 {
  display: none;
}

.extra-sidebar .level2:first-of-type {
  margin-top: 0;
}
```

# Second page sidebar {.aside .extra-sidebar}

## Language Skills {#moreskills}

```{r language_skills, echo=FALSE, warning = FALSE, dev.args = list(bg = 'transparent')}

# function from helper_functions.R
build_skill_bars(skill_data, 'moreskills')

```

## Disclaimer {#disclaimer}

This resume was made with the R package [**pagedown**](https://github.com/rstudio/pagedown).

Last updated on `r Sys.Date()`.